---
title: "Untitled"
author: "22MIA1092"
date: "2023-11-07"
output: html_document
---
```{r}
library(ggplot2)
```
```{r}
data=MASS::survey

```
```{r}
library(MASS)


data("survey")
survey_cleaned <- na.omit(survey)


gender_counts <- table(survey_cleaned$Sex)
barplot(gender_counts, main = "Male and Female Participants", ylab = "Frequency", col = c("blue", "red"))


hand_counts <- table(survey_cleaned$W.Hnd)
barplot(hand_counts, main = "Left Handers and Right Handers", ylab = "Count", col = c("green", "purple"))


left_handed_counts <- table(survey_cleaned$W.Hnd, survey_cleaned$Sex)
barplot(left_handed_counts, beside = TRUE, main = "Female Left Handers and Male Left Handers", ylab = "Count", col = c("blue", "pink"))


hist(survey_cleaned$Age, main = "Age Distribution", xlab = "Age Range", ylab = "Frequency")


plot(survey_cleaned$Age, survey_cleaned$Wr.Hnd, main = "Age vs. Writing Hand Span", xlab = "Age", ylab = "Writing Hand Span")


boxplot(survey_cleaned$Pulse, main = "Pulse Rate Boxplot", ylab = "Pulse Rate")


male_left_handed_smokers <- survey_cleaned$Smoke[survey_cleaned$W.Hnd == "Left" & survey_cleaned$Sex == "Male"]
smoker_counts <- table(male_left_handed_smokers)
pie(smoker_counts, main = "Smoking Habits of Male Left Handers", col = c("green", "red", "blue"))
```

```{r}
data=read.csv(file='/home/ex5/Downloads/iris.csv')
```
```{r}

library(ggplot2)
library(dplyr)
library(corrplot)
library(outliers)


data <- read.csv("iris.csv")


summary(data)


hist(data$Sepal.Length, main = "Histogram of Sepal Length", xlab = "Sepal Length")


plot(data$Sepal.Length, data$Sepal.Width, main = "Scatter Plot of Sepal Length vs Sepal Width", xlab = "Sepal Length", ylab = "Sepal Width")


boxplot(data$Petal.Length ~ data$Species, main = "Boxplot of Petal Length by Species", xlab = "Species", ylab = "Petal Length")


correlation_matrix <- cor(data[, 1:4])
corrplot(correlation_matrix, method = "color")


outliers <- data[outlier(data$Sepal.Length)$ind, ]

print("Outliers:")
print(outliers)

freq_table <- table(data$Species)
print("Frequency Table:")
print(freq_table)



